Performance-portable Parallel Programming in Computer Science Education with Kokkos

### 2020-01-23 main.tex
Updated main.tex to include new tex files.
Some more file name edits.
Further renaming.
Updated authors

\title{Performance-portable Parallel Programming in Computer Science Education with Kokkos and C++}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

@@

\input{src/1.Introduction}        %label: chap:introduction
\input{src/2.Kokkos}              %label: chap:kokkos
\input{src/2.1.KokkosBackend.tex} %label: chap:kokkosBackend
\input{src/3.Exercises}           %label: chap:tutorial
\input{src/4.C++}                 %label: chap:c++
\input{src/5.Related}             %label: chap:related
\input{src/6.Conclusion}          %label: chap:conclusion

>>>>

\title{Performance-portable Parallel Programming in Computer Science Education with Kokkos}

\author{
\IEEEauthorblockN{Jan Ciesko}
\IEEEauthorblockA{\textit{Computer Science Reseach Center} \\
\textit{Sandia National Laboratories}\\
Albuquerque, NM, USA\\
jciesko@sandia.gov}
\and
\IEEEauthorblockN{David Poliakoff}
\IEEEauthorblockA{\textit{Computer Science Reseach Center} \\
\textit{Sandia National Laboratories}\\
Albuquerque, NM, USA\\
dzpolia@sandia.gov}
\and
\IEEEauthorblockN{David S. Hollman}
\IEEEauthorblockA{\textit{Computer Science Reseach Center} \\
\textit{Sandia National Laboratories}\\
Livermore, CA, USA\\
dshallm@sandia.gov}
\and
\IEEEauthorblockN{Author Name}
\IEEEauthorblockA{\textit{Computer Science Reseach Center} \\
\textit{Sandia National Laboratories}\\
Albuquerque, NM, USA\\
aname@sandia.gov}
\and
\IEEEauthorblockN{Author Name}
\IEEEauthorblockA{\textit{Computer Science Reseach Center} \\
\textit{Sandia National Laboratories}\\
Albuquerque, NM, USA\\
aname@sandia.gov}
\and
\IEEEauthorblockN{Author Name}
\IEEEauthorblockA{\textit{Computer Science Reseach Center} \\
\textit{Sandia National Laboratories}\\
Albuquerque, NM, USA\\
aname@sandia.gov}
}

@@

\input{src/1.Introduction}           %label: chap:introduction
\input{src/2.GenericProgramming.tex} %label: chap:background
\input{src/3.MachineModel.tex}             %label: chap:kokkosPM
\input{src/4.ProgammingModel.tex}     %label: chap:kokkosEMA
\input{src/5.Backend.tex}            %label: chap:kokkosBackend
\input{src/6.Exercises}              %label: chap:tutorial
\input{src/7.C++}                    %label: chap:c++
\input{src/8.Related}                %label: chap:related
\input{src/9.Conclusion}             %label: chap:conclusion
